---
#title: '"Singnal Process which produces Higgs bosons and back ground process which does not'""
##author: "Anand-Sujit-Sunil"
##date: "November 28, 2018"
##output: html_document
---
**NOTE** clearing environment

```{r}

rm(list = ls(all=TRUE))

```


```{r}

getwd()

```

```{r}

setwd("C:/Users/DELL/Desktop/cute 2")

```


# Reading the data file
```{r}
cutedata<-read.csv("train_data.csv",header = TRUE)

```

#Take a look at the data using the "head()" and "tail()" functions

```{r}
head(cutedata)
tail(cutedata)

```
#Understand the distribution of various variables in the datset using the "summary()" function

```{r}
summary(cutedata)
```

# Checking for missing values

```{r}
sapply (cutedata,function (x) sum(is.na(x)))

```


#Missing values vs observed
```{r}
library(Amelia)
missmap(cutedata, main = "Missing values vs observed")

```


# Summarize the data (lookwise better)
```{r}
summary(cutedata)
library(mlr)
summarizeColumns(cutedata)

```

# Overview of data
```{r}
str(cutedata)
names(cutedata)
```


# Converting into factor
```{r}
cutedata$class<-as.factor(cutedata$class)
```

# Checking the data to know total no of 1's and 0's for checking imbalance

```{r}
table(cutedata$class)
prop.table(table(cutedata$class))*100

```

# Delete Id from the data (id is identified as by common sense, like phone no)
```{r}

cutedata<-cutedata[-30]
names(cutedata)

```


# Data exploration to see in the bar graph
# aes = asthetics

```{r}
library(ggplot2)
ggplot(cutedata,aes(x=factor(class)))+
  geom_bar(fill='green')

```



#dplyr for filter, sorting
```{r}

library (dplyr)

```

# creating a vector for all the independent variable 
```{r}
inputvar<-c("lepton_phi",
            "missing_energy_magnitude",
            "missing_energy_phi",
            "jet1pt",
            "jet1eta",
            "jet1phi",
            "jet1b.tag",
            "jet2pt",
            "jet2eta",
            "jet2phi",
            "jet2b.tag",
            "jet3pt",
            "jet3eta",
            "jet3phi",
            "jet3b.tag",
            "jet4pt",
            "jet4eta",
            "jet4phi",
            "jet4b.tag",
            "m_jj",
            "m_jjj",
            "m_lv",
            "m_jlv",
            "m_bb",
            "m_wbb",
            "m_wwbb"
)

m <- cor(cutedata[,inputvar])
library(corrplot)
corrplot(m,method = "number") # numerics value bold is high corelatted
corrplot(m,method = "circle") # Big circules is high corelatted

```



# Build a model

## Basic Logistic Regression Model

* Use the glm() function to build a basic model

* Build a model using all the variables, excluding the response variable, in the dataset

* Get the summary of the model and understand the output


```{r}
Model1<-glm(class~.,family=binomial(link=logit),data = cutedata)
library(car)
vif(Model1)
summary(Model1)

# m_wbb has highter VIF so i have removed that variabe from the model

```


```{r}
Model2<-glm(class~lepton_phi+missing_energy_magnitude+missing_energy_phi+jet1pt+jet1eta+jet1phi+jet1b.tag+jet2pt+jet2eta+jet2phi+jet2b.tag+jet3pt+jet3eta+jet3phi+jet3b.tag+jet4pt+jet4eta+jet4phi+jet4b.tag+m_jj+m_jjj+m_lv+m_jlv+m_bb+m_wwbb,family=binomial(link = logit),data=cutedata)
vif(Model2)
summary(Model2)

```

# Removing non significant vairables

```{r}
Model3<-glm(class~missing_energy_magnitude+jet1pt+jet1b.tag+jet2pt+jet2b.tag+jet3pt+jet3b.tag+jet4pt+jet4b.tag+m_jj+m_jjj+m_lv+m_jlv+m_bb+m_wwbb,family=binomial(link = logit),data=cutedata)
summary(Model3)

# all the variables are contributing sifnificantly to the model as they sig is < .05


```

